Molecular dynamics simulation of synchronization in driven particles

### 2021-01-05 manuscript/manuscript_ajp_2020.tex
updated text for new Fig. 2 and suggested new figure (or panel)

In Fig.~\ref{fig:0}(b) 
we show the $y-$position of the particle
as a function of time,
where we 
normalize $y$ by the spatial period of the potential %washboard as
$\lambda$.
The initial particle position is $y=0$,
where the landscape force is minimum $F^l = 0$.
The horizontal dashed lines
coincide with the condition the substrate force is
minimum 
$\sin{(\pi y / \lambda)} = 1 $, so $F^l = -A_p$.
%or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
The crossing of the particle position $y$
with the horizontal and vertical lines
indicates the synchronization
of the driving force with the lattice position of the particle,
where driving force is maximum positive when the
force on the particle from the landscape is maximum negative.
It can be shown this synchronization
occurs for any initial position of $y$.

The slope of $y/\lambda$
is proportional to the net force on the particle (See Eq.~\ref{eq:motion}).
This can be seen in 
Fig.~\ref{fig:0} %we demonstrate this relationship,
where local extrema appear in $y/\lambda$
when $F_{D}(t) \approx 0 $ and 
When $F^D(t) > A_p$, a particle can 
overcome the barrier height of the landscape maxima,
and 
the particle hops between minima in the energy landscape.

the particle moves
in the positive y-direction
through three
substrate troughs, reaching a maximum of $y/\lambda = 3$.
When $F_{D}(t) < 0 $
the particle moves in the negative y-direction
reaching a minimum position
of $y/\lambda = 1$
over the total period $T = 100$.
The average velocity $\bar{v}_y$
is the average displacement $\Delta y = y(t_0+T) - y(t_0)$
over the period of the driving force.
In Fig. ~\ref{fig:0}
the average displacement during one time period is a single wavelength
of the substrate $y(t_0+T) - y(t_0) = \lambda$.
Thus the average velocity 
is $\bar{v}_y = \lambda f$. %, where $T = 1/f$.

>>>>

In Fig.~\ref{fig:0}(b) 
we show the $y-$position of the particle
as a function of time,
where we 
normalize $y$ by the spatial period of the potential %washboard as
$\lambda$.
The initial particle position is $y=0$,
where the landscape force is minimum $F^l = 0$.
The horizontal dashed lines
coincide with the condition the substrate force is
minimum 
$\sin{(\pi y / \lambda)} = 1 $, so $F^l = -A_p$.
%or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
The crossing of the particle position $y$
with the horizontal and vertical lines
indicates the synchronization
of the driving force with the lattice position of the particle,
where driving force is maximum positive when the
force on the particle from the landscape is maximum negative.
It can be shown this synchronization
occurs for any initial position of $y$.
({\it exercise to student})

The slope of $y/\lambda$
is proportional to the net force on the particle (See Eq.~\ref{eq:motion}).
This can be seen in 
Fig.~\ref{fig:0} %we demonstrate this relationship,
where local extrema appear in $y/\lambda$
when $F_{D}(t) \approx 0 $ and 
When $F^D(t) > A_p$, a particle can 
overcome the barrier height of the landscape maxima,
and 
the particle hops between minima in the energy landscape.
In this example
we note 
the particle moves
in the positive y-direction
through $\Delta y = 2 \lambda$ in one time period $\Delta t = T$.
When $F_{D}(t) < 0 $
the particle moves in the negative y-direction 
for a short time.
%reaching a minimum position
%of $y/\lambda = 1$
%over the total period $T = 100$.
The average velocity $\bar{v}_y$
is the average displacement $\Delta y = y(t_0+T) - y(t_0)$
over the period of the driving force.
%In Fig. ~\ref{fig:0}
%the average displacement during one time period is a single wavelength
%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
Thus the average velocity 
is $\bar{v}_y = 2 \lambda f$ where $T = 1/f$.

[add example where particle moves backward].
